### 2020-03-04 submission/manuscript.Rmd
add a line about ML pipeline exercise

The ever-growing ability to generate data and constant feeling of helplessness in analyzing it is analogous to the struggles we also face with engaging the voluminous scientific literature. Within our research group we have leveraged this similarity to address the challenges of training bench scientists to engage in reproducible data analysis practices. Our group and others hold a regular Journal Club to stay current on the literature and model to junior scientists how to engage that literature [@Lonsdale2016]. Over the past 4 years we have experimented with using a Code Club to introduce new software packages, solve specific problems, and evaluate each other's code.

@@

We continue to experiment with approaches to running Code Club. Although any individual Code Club session may be be more experimental than others, on the whole they have been a critical tool to providing the much needed training to use reproducible practices for analyzing data. Examples of successful code club topics are described in Table 1. These Ten Rules summarize what we have learned as presenters and participants.

>>>>

The ever-growing ability to generate data and constant feeling of helplessness in analyzing it is analogous to the struggles we also face with engaging the voluminous scientific literature. Within our research group we have leveraged this similarity to address the challenges of training bench scientists to engage in reproducible data analysis practices. Our group and others hold a regular Journal Club to stay current on the literature and model to junior scientists how to engage that literature [@Lonsdale2016]. Over the past 4 years we have experimented with using a Code Club to introduce new software packages, solve specific problems, and evaluate each other's code in terms of reproducibility.

@@

We continue to experiment with approaches to running Code Club. For example, recently we evaluated a labmate's bioinformatics pipeline to make it more user-friendly so that everyone in the lab could use it for their own projects.  Although any individual Code Club session may be be more experimental than others, on the whole they have been a critical tool to providing the much needed training to use reproducible practices for analyzing data. Examples of successful code club topics are described in Table 1. These Ten Rules summarize what we have learned as presenters and participants.
